\sysfull

### 2018-08-03 paper/asplos19/abstract.tex

Energy harvesting, however, is unpredictable and can only power a device intermittently. Therefore, the two paradigms of intermittent execution (checkpointing and task-based) save intermediate programs states into non-volatile memory frequently, to preserve a program forward progress. Despite the superiority of the task-based approach, however, it fixes their task size at compile time and operates obliviously to the changing energy conditions. When a program divided into tasks for heterogeneous energy buffers it will be persisted either more frequently than necessary or not frequently enough for the program to make progress and terminate. To address these challenges, we propose \sys, an \emph{adaptive} and \emph{efficient} task-based execution model. \sys progresses on a multi-tasks scale, when energy permits and preserves the computation progress on a sub-task scale if necessary. \sys ensures that power failures cannot leave the program state in non-volatile memory inconsistent using a specialized memory virtualization mechanism. Our evaluation shows that \sys is $2X$ faster than the state-of-the-art system in most cases and is able to progress where static systems fail.

>>>>

Energy harvesting, however, is unpredictable and can only power a device intermittently. Therefore, the two paradigms of intermittent execution (checkpointing and task-based) save the intermediate program state into non-volatile memory frequently, to preserve execution progress of a program. Despite the superiority of the task-based approach, however, it fixes the task size at compile time and operates obliviously to changing energy conditions. When tasks are sized without accounting for available energy, state may be persisted either more frequently than necessary or not frequently enough for the program to make progress and terminate.% When a program divided into tasks for heterogeneous energy buffers it will be persisted either more frequently than necessary or not frequently enough for the program to make progress and terminate. 
To address these challenges, we propose \sys, an \emph{adaptive} and \emph{efficient} task-based execution model. \sys progresses on a multi-tasks scale, when energy permits and preserves the computation progress on a sub-task scale if necessary. \sys ensures that power failures cannot leave the program state in non-volatile memory inconsistent using a specialized memory virtualization mechanism. Our evaluation shows that \sys is $2X$ faster than the state-of-the-art system in most cases and is able to progress where static systems fail.
